Functions Created

### 2017-08-23 Hours.Rmd
updated hours

>>>>

8/17/2017 | 3.25 | 9:00-12:15PM | Met with Dr. Pileggi, started researching splines 
8/17/2017 | 1 | 1:30-2:30PM | More spline research
8/21/2017 | 4 | 2:00-6:00PM | Fit splines with univariate analysis, backward/forward selection on model including splines + square root + log transformed variables 
8/22/2017 | 5.5 | 10:00-3:30PM  | Univariate analysis for quadratic terms of variables, fixed setup function, removed devices from frequently answered/answered terms list
8/22/2017 | 3.75 | 6:15-10:00PM | More work with splines + cross validation
